### 2024-08-18 paper.tex
deleting some stuff

\section{Finding the irreducible components of \(U_0\)}
Let \(X\) be nilpotent with Jordan basis \((e_{ij}')_{1 \leq i \leq k, 1 \leq j \leq \lambda_i'}\).
Let \(V = \{(A_{a,b}, U) : \forall i. \; A_{a,b} U_{i + 1} \subseteq U\}\).
Let
\[U_0 = \{(A_{0,b}, U) \in V\}.\]
We will find the irreducible components of \(U_0\).
\par We write \(b_{ij}'\) to denote the projection of \(b \in \mathbb{C}^m\) onto \(e_{ij}'\).
For each row \(i\), let \(p_i'(b) = \max\{j : b_{ij}' \neq 0\}\) (the maximum of the empty set is zero).
Then set \(q_i'(b) = \lambda_i' - p_i'(b)\).
When it is clear enough from context, we will just write \(p_i'\) and \(q_i'\) instead of \(p_i'(b)\) and \(q_i'(b)\).
Then, let \(\{n_1(b), ..., n_k(b)\} = \{1, ..., k\}\) be such that the list 
\[(q_{n_1}', n_1), ..., (q_{n_k}', n_k)\]
is in reverse lexicographical order; that is, for any \(\alpha < \beta\), we have either \(q_{n_\alpha}' > q_{n_\beta}'\) or \(q_{n_\alpha}' = q_{n_\beta}' \land n_\alpha > n_\beta\).
The point is that we want the list \(q_{n_1}', ..., q_{n_k}'\) to be nonincreasing.
To break ties in an arbitrary canonical way, we say that if \(q_\gamma' = q_\delta'\), then we put the one with the bigger subscript first.
\par Now, in the rest of this section it will be convenient for us to have the values \(q_i'\) in nonincreasing order.
To avoid death by double subscript, we define \(e_{ij}(b) := e_{n_ij}'\), \(\lambda_i(b) := \lambda_{n_i}'\), \(p_i(b) := p_{n_i}'\), \(q_i(b) := q_{n_i}'\).
\par TODO: try to introduce the same notation less obnoxiously.
\par For any \(I' \subseteq \{1, ..., k\}\) and any values \((\rho_i')_{i \in I'}\) such that (1) \(\rho_i' \leq \lambda_i\) and (2) \(\rho_i'\) is decreasing with \(i\), define 
\[U_{I', (\rho_i')} := \{(A_{0, b}, U) \in U_0 : I' = \{n_i : p_i > \max_{j > i} p_j\} \land \forall i \in I'. \; p_i = \rho_{n_i}' \}.\]
\begin{lemma}
    \(U_0 = \bigcup_{I', (\rho_i')} U_{I', (\rho_i')}\), where \(I'\) ranges over all possible subsets of \(\{1, ..., k\}\), and \((\rho_i')\) ranges over all possible maps \(I' \to \mathbb{N}_{>0}\) such that \(\rho_i'\) is decreasing as \(i\) increases.
\end{lemma}
\begin{proof}
    Let \((A_{0, b}, U) \in U_0\).
    Define \(I' := \{n_i : p_i > \max_{j > i} p_j\}\), and for \(n_i \in I'\), \(\rho_{n_i}' := p_i\).
    All we need to do is show that each \(\rho_i'\) is positive and that \(\rho_i'\) is decreasing.
    Then we get that \((A_{0,b}, U) \in U_{I', (\rho_i')}\), and we are done.
    \par Recall that by convention the maximum of the empty set is zero.
    So, the fact that \(p_i > \max_{j > i} p_j\) tells us that \(\rho_{n_i}' = p_i\) is positive.
    Now, let \(n_i < n_{i'}\), with \(n_i, n_{i'} \in I'\).
    We have \(p_i > \max_{j > i} p_j\); that is, \(\) AGH CONFUSION
    We have two cases: either \(i < i'\), or \(i' < i\).
    If we had \(p_i \leq p_{i'}\), then \(q_i \geq q_{i'}\)

>>>>

\section{Finding the irreducible components of \(U_0\)}
Let \(X\) be nilpotent with Jordan basis \((e_{ij}')_{1 \leq i \leq k, 1 \leq j \leq \lambda_i'}\).
Let \(V = \{(A_{a,b}, U) : \forall i. \; A_{a,b} U_{i + 1} \subseteq U\}\).
Let
\[U_0 = \{(A_{0,b}, U) \in V\}.\]
We will find the irreducible components of \(U_0\).
\par We write \(b_{ij}'\) to denote the projection of \(b \in \mathbb{C}^m\) onto \(e_{ij}'\).
For each row \(i\), let \(p_i'(b) = \max\{j : b_{ij}' \neq 0\}\) (the maximum of the empty set is zero).
Then set \(q_i'(b) = \lambda_i' - p_i'(b)\).
When it is clear enough from context, we will just write \(p_i'\) and \(q_i'\) instead of \(p_i'(b)\) and \(q_i'(b)\).
Then, let \(\{n_1(b), ..., n_k(b)\} = \{1, ..., k\}\) be such that the list 
\[(q_{n_1}', n_1), ..., (q_{n_k}', n_k)\]
is in reverse lexicographical order; that is, for any \(\alpha < \beta\), we have either \(q_{n_\alpha}' > q_{n_\beta}'\) or \(q_{n_\alpha}' = q_{n_\beta}' \land n_\alpha > n_\beta\).
The point is that we want the list \(q_{n_1}', ..., q_{n_k}'\) to be nonincreasing.
To break ties in an arbitrary canonical way, we say that if \(q_\gamma' = q_\delta'\), then we put the one with the bigger subscript first.
\par Now, in the rest of this section it will be convenient for us to have the values \(q_i'\) in nonincreasing order.
To avoid death by double subscript, we define \(e_{ij}(b) := e_{n_ij}'\), \(\lambda_i(b) := \lambda_{n_i}'\), \(p_i(b) := p_{n_i}'\), \(q_i(b) := q_{n_i}'\).
\par TODO: try to introduce the same notation less obnoxiously.
\par For any \(I' \subseteq \{1, ..., k\}\) and any values \((\rho_i')_{i \in I'}\) such that (1) \(\rho_i' \leq \lambda_i\) and (2) \(\rho_i'\) is decreasing with \(i\), define 
\[U_{I', (\rho_i')} := \{(A_{0, b}, U) \in U_0 : I' = \{n_i : p_i > \max_{j > i} p_j\} \land \forall i \in I'. \; p_i = \rho_{n_i}' \}.\]
\begin{lemma}
    \(U_0 = \bigcup_{I', (\rho_i')} U_{I', (\rho_i')}\), where \(I'\) ranges over all possible subsets of \(\{1, ..., k\}\), and \((\rho_i')\) ranges over all possible maps \(I' \to \mathbb{N}_{>0}\) such that the maps \(i \mapsto \rho_i'\) and \(i \mapsto \lambda'_i - \rho_i'\) are both decreasing with \(i\).
\end{lemma}
\begin{proof}
    Let \((A_{0, b}, U) \in U_0\).
    Define \(I := \{i : p_i > \max_{j > i} p_j\}\), and let \(I' := \{n_i : i \in I\}\).
    And for \(i \in I\), \(\rho_{n_i}' := p_i\).
    All we need to do is show that each \(\rho_i'\) is positive and that \(\rho_i'\) is decreasing.
    Then we get that \((A_{0,b}, U) \in U_{I', (\rho_i')}\), and we are done.
    \par Recall that by convention the maximum of the empty set is zero.
    So, the fact that \(p_i > \max_{j > i} p_j\) tells us that \(\rho_{n_i}' = p_i\) is positive.
    \par For \(i, j \in I\) with \(i < j\), we have \(q_i \geq q_j\) (as \(q\) is nonincreasing), and also \(p_i > p_j\) (as \(i \in I\), and consequently \(p_i > \max_{l > i} p_l\)).
    Thus, \(\lambda_i > \lambda_j\).
